Measuring Political Freedom Around the World

### 2020-11-24 slides.Rmd
rm plot
worked on slides

style_mono_accent_inverse(base_color = "#3C989E")
theme_set(theme_light(base_size = 30))
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE, fig.width = 12, fig.height = 8)

@@

* We ask: What factors are associated with an increase in political freedom?.

@@

* Filtered to only include OECD Countries from year 2000 to 2018 by necessity.

@@

- Corruption Perception Index ranges from 0 to 100 with 0 being the highest perception of corruption

@@

- Education Expenditure in GDP per Person

@@

- Electricity use per person in Kilowatt Hours

@@

- Gini Coefficient: A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth

@@

- Percentage of population That use the Internet

@@

- Labor Force Participation

@@

- Life Expectancy

@@

- Military Spending as a percentage of GDP

@@

- Murders per million people

@@

```{r}
data %>% 
  ggplot(aes(x = year, y = polrights_fh)) + 
  geom_col() +
  facet_wrap(~country) + 
  coord_flip() + 
  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
  scale_x_continuous(breaks = 1:7) + 
  theme(legend.position = "none")
  theme_light(base_size = 12)
```
---

@@

# Best Subsets by Adjusted R Squared
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, Model) %>%
  arrange(desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3), 
              colnames = c("DF", "$$R^{2}_a$$", "Model"))
```

---
# Best Subsets by AIC
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(AIC == min(AIC)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(df, AIC, Model) %>% 
  arrange(AIC) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
              colnames = c("DF", "AIC", "Model"))
```

# Best Subsets by BIC
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(BIC == min(BIC)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(df, BIC, Model) %>% 
  arrange(BIC) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
              colnames = c("DF", "BIC", "Model"))
```

@@

# Best Subsets

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "#3C989E") + 
  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_test(base_size = 30) 
  #    +  
```

# Best Subsets

@@

subsets %>% 
  ggplot(aes(x = df, y = AIC)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "#3C989E") + 
  labs(title = "", x = "Parameters", y = "AIC") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_test(base_size = 30) 
  #    +  
```

@@

class: inverse, middle, center

# Model

class: center, middle
```{r}
model_df5_formula <- subsets %>% filter(df == 5) %>% 
  arrange(desc(adj.r.squared)) %>% 
  select(model) %>% head(1) %>% as.character()

@@

$$
\large
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
---
class: center

$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$

@@

---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"))  %>%
  row_spec(2, color = "white", background = "#3C989E")
```

@@

---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(3, color = "white", background = "#3C989E")
```

@@

---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(4, color = "white", background = "#3C989E")
```

@@

class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(5, color = "white", background = "#3C989E")
```

@@

class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(6, color = "white", background = "#3C989E")
```

@@

```{r warning=FALSE}

hist <- fit_df5 %>% 
  broom::augment() %>% 
  ggplot(aes(.resid)) + 
  geom_histogram(bins = 100) +
  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")

qq <- fit_df5 %>% 
  broom::augment() %>% 
  ggplot(aes(sample = .resid)) + 
  stat_qq() +
  stat_qq_line() + 
scale_x_continuous(limits = c(-4,4)) + 
scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected")   
```

@@

```{r}
data %>% 
  filter(polrights_fh >= 4) %>% 
  lm(model_df5_formula, .) %>% 
  broom::tidy() %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"),
        caption = "Removed Outliers") 
```

@@

- We identified these outliers.
- Confirmed they are not errors. 
- Decided to keep them because they are indicating a substantial loss in political freedom which falls outside of the scope of the model. However, is important for our research question.
***
> "A safe rule frequently suggested is to discard an outlier only if there is direct evidence that it represents an error in recording, a miscalculation, a malfunctioning of equipment, or a similar type of circumstance". -Chapter 3 p.108

@@

- Conclude again error variance is not constant even when outliers are removed

@@

1. we think this
1. because

>>>>

style_mono_accent_inverse(base_color = "#3C989E")
theme_set(theme_light(base_size = 30))
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE, fig.width = 12, fig.height = 8)

@@

* We ask: What factors are associated with an increase in political freedom?

@@

* Filtered to only include OECD Countries from year 2000 to 2018 by necessity.
--

* Made adjustments for more intuitive interpretations.

@@

- **Corruption Perception** Index ranges from 0 to 100 with 100 being the highest perception of corruption

@@

- **Education Expenditure** in GDP per Person

@@

- **Electricity use** per person in Kilowatt Hours

@@

- **Gini Coefficient:** A measure of a nation's wealth inequality ranging from 0 being perfectly equal distribution of income and 1 being one person has all nation's wealth

@@

- **Internet Users** as percentage of Population

@@

- **Labor Force** Participation rate

@@

- **Life Expectancy**

@@

- **Military Spending** as a percentage of GDP

@@

- **Murders rate** per million people

@@

@@

# Best Subsets by Adjusted R Squared
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, Model) %>%
  arrange(match(df, c(5, 4, 6)), desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3), 
              colnames = c("DF", "$$R^{2}_a$$", "Model"))
```
---
class: center, middle

# Best Subsets by Adjusted R Squared

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "#3C989E") + 
  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_test(base_size = 30) 
```

---
# Best Subsets by AIC
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(AIC == min(AIC)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  select(df, AIC, Model) %>% 
  arrange(match(df, c(5, 4, 6)), desc(AIC)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3),
              colnames = c("DF", "AIC", "Model"))
```

@@

# Best Subsets by AIC

@@

subsets %>% 
  ggplot(aes(x = df, y = AIC)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, AIC), se = FALSE, span = 0.5, color = "#3C989E") + 
  labs(title = "", x = "Parameters", y = "AIC") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_test(base_size = 30) 
```

@@

class: inverse, center
# Model
```{r}
model_df5_formula <- subsets %>% filter(df == 5) %>% 
  arrange(desc(adj.r.squared)) %>% 
  select(model) %>% head(1) %>% as.character()

@@

$$
\large
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
---
class: center
$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$

```{r message=FALSE}
size <- 18
a <- data %>% 
  ggplot(aes(x = corruption_perception_index_cpi, y = polrights_fh)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
  scale_y_continuous(breaks = 1:7) + 
  labs(x = "Corruption Perception", y = "Political Rights") + theme_light(base_size = size)

b <- data %>% 
  ggplot(aes(x = edu_exp_gdp_per_person, y = polrights_fh)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") +
    scale_y_continuous(breaks = 1:7) + 
  labs(x = "Education Expendature", y = "") + theme_light(base_size = size)

c <- data %>% 
  ggplot(aes(x = life_expectancy_years, y = polrights_fh)) + 
  geom_point()+ 
  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") +
    scale_y_continuous(breaks = 1:7) + 
  labs(x = "Life Expectacy", y = "") + theme_light(base_size = size)

d <- data %>% 
  ggplot(aes(x = military_spending_pct_of_gdp, y = polrights_fh)) + 
  geom_point()+ 
  scale_y_continuous(breaks = 1:7) + 
  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
  labs(x = "Military Spending", y = "")+ theme_light(base_size = size)

e <- data %>% 
  ggplot(aes(x = murder_per_mil_people, y = polrights_fh)) + 
  geom_point() + 
  scale_y_continuous(breaks = 1:7) + 
  geom_smooth(method = "lm", se = FALSE, color = "#3C989E") + 
  labs(x = "Murder Rate", y = "") + theme_light(base_size = size)

(a + b) / (c + d + e) 
```

$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
# Correlation Matrix
```{r}
corr_matrix <- data %>%
  select(polrights_fh,corruption_perception_index_cpi,edu_exp_gdp_per_person,life_expectancy_years,military_spending_pct_of_gdp,murder_per_mil_people) %>% 
  cor()

rownames(corr_matrix) <- c("Political Rights", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")
colnames(corr_matrix) <-  c("Political Rights", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")
kable(round(corr_matrix, 2)) %>% 
  kable_styling(font_size = 12)
```

$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$

@@

---
class: center
$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"))  %>%
  row_spec(2, color = "white", background = "#3C989E")
```

@@

---
class: center
$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(3, color = "white", background = "#3C989E")
```

@@

---
class: center
$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(4, color = "white", background = "#3C989E")
```

@@

class: center
$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(5, color = "white", background = "#3C989E")
```

@@

class: center
$$
\scriptsize
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(fit_df5) %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  mutate(term = c("(Intercept)", "Corruption Perception", "Education Expendature", "Life Expectancy", "Military Spending", "Murder Rate")) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value")) %>% 
  row_spec(6, color = "white", background = "#3C989E")
```

@@

```{r}

hist <- fit_df5 %>% 
  broom::augment() %>% 
  ggplot(aes(.resid)) + 
  geom_histogram(bins = 75, fill = "black") +
  scale_x_continuous(limits = c(-4,4)) + labs(y = "Density", x = "Residual", title = "Histogram")

qq <- fit_df5 %>% 
  broom::augment() %>% 
  ggplot(aes(sample = .resid)) + 
  stat_qq() +
  stat_qq_line(color = "#3C989E") + 
scale_x_continuous(limits = c(-4,4)) + 
scale_y_continuous(limits = c(-4,4)) + labs(title = "QQ Plot of Residuals ", x = "Residual", y = "Expected")   
```

@@

```{r}
data %>% 
  filter(polrights_fh >= 4) %>% 
  lm(model_df5_formula, .) %>% 
  broom::tidy() %>% 
  mutate(p.value = as.character(p.value)) %>%
  mutate_if(is.numeric, round, 3) %>% 
  mutate(p.value = as.numeric(p.value)) %>% 
  kable(col.names =  c("Term", "Estimate", "Std. Error", "T-Stat", "P-Value"),
        caption = "Removed Outliers")

vars <- rownames(summary(fit_df5)$coef)
vars[1] <- "polrights_fh"
```

@@

> "A safe rule frequently suggested is to discard an outlier only if there is direct evidence that it represents an error in recording, a miscalculation, a malfunctioning of equipment, or a similar type of circumstance". -Chapter 3 p.108

***
- We identified these outliers.
- Confirmed they are not errors. 
- Decided to keep them because they are indicating a substantial loss in political freedom which falls outside of the scope of the model. However, is important for our research question.

@@

- Conclude, again, error variance is not constant even when outliers are removed.
- The model does a much better job at predicting political freedom in countries with more. This is likely due to the fact that our sample is the OCED that skews twards more Political Freedom

@@

1. Despite minor problems with outliers we found that statistically significant 
1. because
